Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-20 paper/structureScene.tex
Edit results

The same observations are made for the MFCCs for $k\leq5$. However for a rank $k$ greater than $5$, all the \emph{RbQ} approaches perform equivalently. As such, one can conclude that the use of MFCCs allows us to retrieve closely related scenes, but their lack of discriminative capabilities making the cluster selection/weighting step useless for not so closely related scenes of the same class

>>>>

The same observations are made for the MFCCs for $k\leq5$. However for a rank $k$ greater than $5$, all the \emph{RbQ} approaches perform equivalently. As such, one can conclude that the use of MFCCs allows us to retrieve closely related scenes, but their lack of discriminative capabilities making the cluster selection/weighting step useless for not so closely related scenes of the same class.
